\begin{rubric}{Academic Positions}
    \entry*[] \textbf{Teaching at a private university}, Universidad Austral \hspace{1mm}$\mid$\hspace{1mm} Aug 2025 -- Nov 2025.
    \begin{itemize}
        \itemsep0em
        \item Taught curriculum about programming paradigms: Haskell, Prolog, Python and Erlang. Designed it from scratch.
    \end{itemize}
    \entry*[] \textbf{Teaching at a private university}, Universidad Austral \hspace{1mm}$\mid$\hspace{1mm} Mar 2024 -- Nov 2025.
    \begin{itemize}
        \itemsep0em
        \item Taught the foundations of programming with Python, created brand new exercises.
        \item Taught web development using Angular.
    \end{itemize}
    \entry*[] \textbf{Student Teaching Assistant}, Universidad Nacional de Rosario \hspace{1mm}$\mid$\hspace{1mm} Mar 2022 -- Nov 2023.
    \begin{itemize}
        \itemsep0em
        \item Taught the foundations of programming with Python.
        \item Taught data structures, algorithms and graph theory, applied to Python programming.
    \end{itemize}
    \entry*[] \textbf{High School Substitute Teacher}, Instituto Politécnico Superior \hspace{1mm}$\mid$\hspace{1mm} Mar 2022 -- Nov 2025.
    \begin{itemize}
        \itemsep0em
        \item Taught foundations of informatics to 1st-year students, created brand new teaching material.
        \item Taught spreadsheets and blocks-based programming to 2nd-year students, revised existing teaching material.
        \item Taught C programming to 4th-year students, revised existing teaching material and exercises.
        \item Taught Haskell programming, algorithms, and data structures to 5th-year students. Designed the curriculum from scratch.
    \end{itemize}
\end{rubric}