\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}

% Geometry settings for standard French letter margins
\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=20mm,
  bottom=20mm,
}

% Sender Information
\name{Luciano Barletta}
\signature{Luciano Barletta}
\address{Luciano Barletta \\ Oroño 5845 B \\ Rosario, Santa Fe, Argentina \\ \faEnvelope\ \href{mailto:lushobarlett@gmail.com}{lushobarlett@gmail.com} \\ \faPhone\ +54 341 595-9169 }

% Date
\date{\today}

\begin{document}

% Recipient Information - Updated for Inria Nancy / MOCQUA
\begin{letter}{
		\textbf{Inria Nancy -- Grand Est} \\
		Équipe-projet MOCQUA \\
		615 rue du Jardin Botanique \\
		54600 Villers-lès-Nancy, France
	}

	\opening{Dear Members of the Selection Committee,}

	% Object Line - Specific to the offer
	\noindent\textbf{Subject:} Application for PhD Position -- Resource-Aware Quantum Lambda Calculi with Coherent Control (PEPR EPiQ)
	\vspace{0.5cm}

	% --- PART 1: LE VOUS (The Context) ---
	% Focus: Specific research interest
	I am submitting my candidacy for the position referenced above. I am interested in this research line because it targets formal certification of resource consumption in quantum programs. Using linear logic and realizability techniques to characterize classes like BQP is a concrete problem I want to work on.

	In my Master's thesis, I worked independently to design and implement a functional quantum programming language. I focused on the "classical control / quantum data" paradigm, defined semantics using superoperators and density matrices to model measurements and loops, implemented an interpreter in Haskell, and adapted a Hoare Logic for verification. I maintained excellent academic standing throughout my studies, which provided a solid base in complexity theory and formal methods.

	% --- PART 3: LE NOUS (The Fit) ---
	% Focus: Technical Match
	My experience with functional programming and quantum semantics is directly applicable to this project. I am prepared to investigate the challenges posed by coherent control and to contribute to the development of sound type systems for quantum complexity.

	% --- CLOSING ---
	\vspace{0.5cm}
	I have enclosed my CV for your review.
	% Mandatory French formal closing
	\closing{Je reste à votre disposition pour un entretien et vous prie d'agréer, Madame, Monsieur, l'expression de mes salutations distinguées.}

\end{letter}
\end{document}
