\begin{rubric}{Work Experience}
\entry*[] \textbf{Software Engineer}, STC \hspace{1mm}$\mid$\hspace{1mm} Jan 2025 -- Present.
\begin{itemize}
    \itemsep0em
    \item Designed and implemented a high-performance FIX messaging client for Argentina’s main exchange, using Python and a custom integration over a FIX engine.
    \item Delivered production-grade reliability under tight latency requirements; validated against real market feeds.
    \item Coordinated directly with stakeholders and the local exchange to deploy and validate the trading connectivity stack.
\end{itemize}
\entry*[] \textbf{Tooling Engineer}, Province of Santa Fe \hspace{1mm}$\mid$\hspace{1mm} Jan 2025 -- Jul 2025.
\begin{itemize}
    \itemsep0em
    \item Architected a highly automated Android device provisioning pipeline for secure communication systems used in regional elections.
    \item Rewrote critical automation components in Python and replaced legacy C cryptographic routines with up-to-date primitives.
    \item Introduced a secure key-handling workflow across the tooling chain for PDF signing.
    \item Improved image processing and reduced failed PDF generation by half.
\end{itemize}
\entry*[] \textbf{Full Stack Developer}, Province of Buenos Aires \hspace{1mm}$\mid$\hspace{1mm} Feb 2024 -- Dec 2024.
\begin{itemize}
    \itemsep0em
    \item Led the performance redesign of a large-scale data analytics platform aggregating millions of educational records across thousands of institutions.
    \item Built a novel query builder enabling domain experts to generate optimized analytical queries; reduced worst-case query times from minutes to 1–3 seconds.
    \item Designed indexes, partitions, and caching strategies improving backend throughput $>10\times$ under real workloads.
    \item Collaborated closely with product stakeholders to deliver features on tight deadlines.
\end{itemize}
\entry*[] \textbf{Full Stack Developer}, IPS (UNR) \hspace{1mm}$\mid$\hspace{1mm} Apr 2021 -- Present.
\begin{itemize}
    \itemsep0em
    \item Designed and built a full production web platform used by students, parents, and administrative staff (React + TypeScript + Tailwind + Express + Prisma + PostgreSQL).
    \item Implemented modules for grades, attendance, academic planning, calendar orchestration, and multi-role access control.
    \item Developed a highly maintainable $\approx$30 KLOC codebase; platform operates with $\approx$5,000 concurrent users during peak hours.
    \item Migrated legacy workflows to a modern cloud-ready architecture.
\end{itemize}
\entry*[] \textbf{Lecturer / Course Designer}, Austral University \hspace{1mm}$\mid$\hspace{1mm} Mar 2024 -- Present.
\begin{itemize}
    \itemsep0em
    \item Designed and taught curriculum covering Python, Angular, Haskell, Prolog, Erlang, and programming paradigms (functional, declarative/logical, OO, concurrent).
    \item Created advanced teaching material and graded technical assignments for 100+ students a year.
    \item Provided strong theoretical background that complements industry engineering.
\end{itemize}
\entry*[] \textbf{Lecturer}, IPS \& UNR \hspace{1mm}$\mid$\hspace{1mm} Mar 2022 – Present
\begin{itemize}
    \itemsep0em
    \item Taught courses in Python, C, Haskell, and algorithmic problem solving; authored new problem sets and competitive-programming-style exercises.
\end{itemize}
\end{rubric}